Figures

### 2016-08-15 ms_1_intro.Rmd
pushing to merge with remote edits

<!--
The two datasets ostensibly describe the same information, but significant differences in methodology and intent could lead to dramatically different understandings of our marine ecosystems, with significant implications for policy and conservation recommendations. 
Discuss "truth" and uncertainty in species distributions.
There is an objective "truth"; 
-->
Neither dataset claims to represent the "truth" of a species' spatial distribution, but rather each presents one understanding of the "truth" - one database relying primarily on expert opinion and the other on model predictions.  Uncertainties inherent in the method and intent inevitably drive differences in the range predictions made by each dataset; significant differences could ___lead to, communicate, imply___ dramatically different understandings of our marine ecosystems, with significant implications for policy and conservation recommendations.

Importantly, biases in taxonomic or spatial coverage within a dataset could shift management and conservation actions away from places or species that are most in need.  Inaccurate indications of presence or absence could lead to ineffective marine reserve systems and management plans [@rondinini_tradeoffs_2006; @jetz_ecological_2008].

@@

It seems fair to assume that range predictions from each dataset would be more closely aligned for well-understood species.  For the `r format(n_spp_both, big.mark = ',')` species (`r p_both_all`% of total) mapped in both datasets, we examine how well the maps align, determine several issues that lead to misalignment between predicted species distributions, and suggest methods to improve confidence in species range predictions.

@@

___we are not recommending one data set as better than the other!___

>>>>

<!--
The two datasets ostensibly describe the same information, but significant differences in methodology and intent could lead to dramatically different understandings of our marine ecosystems, with significant implications for policy and conservation recommendations. 
Discuss "truth" and uncertainty in species distributions.
There is an objective "truth"; 
-->
Neither dataset claims to represent the "truth" of a species' spatial distribution, but rather each presents one understanding of the "truth" - one database relying primarily on expert opinion and the other on model predictions.  Uncertainties inherent in the method and intent inevitably drive differences in the range predictions made by each dataset; significant differences could indicate dramatically different understandings of our marine ecosystems, with significant implications for policy and conservation recommendations.

Inaccurate indications of presence or absence could lead to ineffective marine reserve systems and management plans [@rondinini_tradeoffs_2006; @jetz_ecological_2008].  Importantly, biases in taxonomic or spatial coverage within a dataset could shift management and conservation actions away from places or species that are most in need.

@@

___It seems fair to assume that/we can reasonably assume that___ range predictions from each dataset would be more closely aligned for well-understood species.  For the `r format(n_spp_both, big.mark = ',')` species (`r p_both_all`% of total) mapped in both datasets, we examine how well the maps align, determine several issues that lead to misalignment between predicted species distributions, and suggest methods to improve confidence in species range predictions.

@@

While we cannot recommmend one data set as more accurate than the other, we suggest methods to improve confidence in species range predictions to better inform conservation management and policy decisions.

### 2016-08-15 ms_2_methods.Rmd
pushing to merge with remote edits

The IUCN publishes species range maps based on expert input of spatial boundaries of a given species' "limits of distribution" [@iucn_iucn_2015] - essentially a refined extent of occurrence (EOO), based on observation records and informed by expert understanding of species' range and habitat preferences.  In contrast, AquaMaps models species distribution based on environmental preferences (e.g., temperature, depth, salinity) deduced from occurrence records, published species databases such as FishBase, and expert knowledge.  The AquaMaps model overlays these environmental preferences atop a map of environmental attributes on a 0.5 degree grid, creating a global map of "probability of occurrence" for each species [@kaschner_mapping_2006; @ready_predicting_2010].  Studies using AquaMaps data frequently define "presence" by applying a probability threshold, e.g., the Ocean Health Index defines presence as 40% or greater probability of occurrence [@halpern_index_2012; @halpern_patterns_2015].

>>>>

The IUCN publishes species range maps based on expert input of spatial boundaries of a given species' "limits of distribution" [@iucn_iucn_2015] - essentially a refined extent of occurrence (EOO), based on observation records and informed by expert understanding of species' range and habitat preferences.  In contrast, AquaMaps models species distribution based on environmental preferences (e.g., temperature, depth, salinity) deduced from occurrence records, published species databases such as FishBase, and expert knowledge.  The AquaMaps model overlays these environmental preferences atop a map of environmental attributes on a 0.5 degree grid, creating a global map of suitable habitat.  The model masks habitat to certain FAO Major Fishing Areas as a rough cut of geographic range, resulting in a "probability of occurrence" for each species.  Of the resulting maps, 1296 (5.7%) have been further refined under expert review [@kaschner_mapping_2006; @ready_predicting_2010].  Studies using AquaMaps data frequently define "presence" by applying a probability threshold, e.g., the Ocean Health Index defines presence as 40% or greater probability of occurrence [@halpern_index_2012; @halpern_patterns_2015].

___short paragraph about other datasets we didn't include, i.e. SAUP?___
